\huge{Comment on `The Limits of Cosmic Shear'}

### 2016-12-07 cfhtlens.tex
minor changes to cfhtlens.tex
minor update and comment

\citet{kitching/etal:2016} choose to only vary $\sigma_8$ in their analysis, fixing all other parameters to their Planck values. They find a conditional value of $\sigma_8 = 0.789 \pm 0.015$ for their `standard' analysis (row 1 in Table~\ref{tab:Tl_nu}) of the data from \citet{kilbinger/etal:2013}.    This can be compared to the full five-parameter fit from \citet{kilbinger/etal:2013} who find $S_8=\sigma_8(\Omega_m/0.3)^{0.6} = 0.74 \pm 0.03$.   We argue that this reduction in the relevant error by a factor of $\sim 2$, could easily mislead, making it appear that the impact of removing all approximations from the theoretical analysis is more significant for current surveys than it is in reality.  Nevertheless, we repeated the `one-parameter' analysis for the full range of Limber cases listed in Table~\ref{tab:Tl_nu} and are unable to confirm the results quoted by \citet{kitching/etal:2016} {\bf TBD:  The results that follow use the exact Planck 2015 cosmology.  We just noticed footnote 5 in Kitching et al that shows that they've actually used an approximate Planck 2015 cosmology - currently re-running with this alternative which is unlikely to change these results significantly}.  We find the lowest conditional value of $\sigma_8 = 0.743 \pm 0.023$ for the `Standard' (KSt) case and the highest conditional value of $\sigma_8 = 0.744 \pm 0.023$ for the `Baseline Limber Flat` (LF) case, noting that fluctuations between different MCMC runs are of the order 0.001.  Therefore, as expected from the comparison in Figure~\ref{fig:Cl_xi}, and given the low signal-to-noise CFHTLenS measurements on large scales, we find that the different combinations of assuming flat or spherical sky, baseline or extended Limber, make little difference to the cosmological parameter constraints, even in this `one-parameter' analysis.

Our Limber-case findings are in disagreement with \citet{kitching/etal:2016} who find a shift of $\Delta \sigma_8 = 0.007$ between their `standard' analysis (row 1 in Table~\ref{tab:Tl_nu}) and their `Limber' analysis (which we believe corresponds to the Extended Limber spherical (ELS) case in Table~\ref{tab:Tl_nu}).

@@

\begin{figure}[htb]
\begin{center}
\begin{tabular}{ccc}
\includegraphics[width=0.31\textwidth]{figures/IntegKsip.pdf} &
\includegraphics[width=0.31\textwidth]{figures/IntegCOSEBIs.pdf} &
\includegraphics[width=0.31\textwidth]{figures/IntegMap.pdf}
\end{tabular}
\caption{ \label{fig:filters}. Integrand of $\xi_+$, $E_1$ (E-COSEBIs) and $M^2_{\rm ap}$, respectively.
All integrands are of the form $\ell F(\ell) P(\ell)$, where $F(\ell)$ is the corresponding weight-function
for each statistic and $P(\ell)$ is the E-mode convergence power spectrum, with the exception of $\xi_+$, for which
$P(\ell)$ is equal to the sum of E and B-mode power spectra. 
Two cases are shown for each statistic as listed in each caption.
For the aperture mass statistic $\theta_{\rm max}=2\theta$ is shown. 
Note that higher order COSEBIs modes generally probe larger $\ell$-modes, 
hence here we only show the lowest mode $E_1$. All values are normalized with respect to their maximum value. 
}
\end{center}
\end{figure}

>>>>

\citet{kitching/etal:2016} choose to only vary $\sigma_8$ in their analysis, fixing all other parameters to their Planck values. They find a conditional value of $\sigma_8 = 0.789 \pm 0.015$ for their `standard' analysis (row 1 in Table~\ref{tab:Tl_nu}) of the data from \citet{kilbinger/etal:2013}. This can be compared to the full five-parameter fit from \citet{kilbinger/etal:2013} who find $S_8=\sigma_8(\Omega_m/0.3)^{0.6} = 0.74 \pm 0.03$.   We argue that this reduction in the relevant error by a factor of $\sim 2$, could easily mislead, making it appear that the impact of removing all approximations from the theoretical analysis is more significant for current surveys than it is in reality.  Nevertheless, we repeated the `one-parameter' analysis for the full range of Limber cases listed in Table~\ref{tab:Tl_nu} and are unable to confirm the results quoted by \citet{kitching/etal:2016}. 
%{\bf TBD:  The results that follow use the exact Planck 2015 cosmology.  We just noticed footnote 5 in Kitching et al that shows that they've actually used an approximate Planck 2015 cosmology - currently re-running with this alternative which is unlikely to change these results significantly}.  
We find the lowest conditional value of $\sigma_8 = 0.7461 \pm 0.0231$ for the `Standard' (KSt) case and the highest conditional value of $\sigma_8 = 0.7487 \pm 0.0232$ for the `Baseline Limber Flat` (LF) case. Comparing the fiducially used `Extended Standard Flat` (ESt) case with the preferred `Extended Limber Spherical` (ELS) case, the constraints are identical at the $0.01\sigma$ level.
Therefore, as expected from the comparison in Figure~\ref{fig:Cl_xi}, and given the low signal-to-noise CFHTLenS measurements on large scales, we find that the different combinations of assuming flat or spherical sky, baseline or extended Limber, make little difference to the cosmological parameter constraints, even in this `one-parameter' analysis.

Our Limber-case findings are in disagreement with \citet{kitching/etal:2016} who find a shift of $\Delta \sigma_8 = 0.007$ between their `standard' analysis (row 1 in Table~\ref{tab:Tl_nu}) and their `Limber' analysis (which we believe corresponds to the Extended Limber spherical (ELS) case in Table~\ref{tab:Tl_nu}).  
\shahab{(I believe Tom in the latest email claimed the 0.007 number is between ESt and ELS)}

@@

\begin{figure}[htb]
\begin{center}
\begin{tabular}{ccc}
\includegraphics[width=0.325\textwidth]{figures/IntegKsip.pdf} 
\includegraphics[width=0.325\textwidth]{figures/IntegCOSEBIs.pdf} 
\includegraphics[width=0.325\textwidth]{figures/IntegMap.pdf}
\end{tabular}
\caption{ \small{\label{fig:filters}. Integrand of $\xi_+$, $E_1$ (E-COSEBIs) and $M^2_{\rm ap}$, respectively.
All integrands are of the form $\ell F(\ell) P(\ell)$, where $F(\ell)$ is the corresponding weight-function
for each statistic and $P(\ell)$ is the E-mode convergence power spectrum, with the exception of $\xi_+$, for which
$P(\ell)$ is equal to the sum of E and B-mode power spectra. 
Two cases are shown for each statistic as listed in each caption.
For the aperture mass statistic $\theta_{\rm max}=2\theta$ is shown. 
Note that higher order COSEBIs modes generally probe larger $\ell$-modes, 
hence here we only show the lowest mode $E_1$. All values are normalized with respect to their maximum value. }
}
\end{center}
\end{figure}
